---
title: '%TASK%'
subtitle: 'Task report'
author: '%AUTHOR%'
date: '%DATE%'
output: 
  pdf_document:
    number_sections: true
    toc: true
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[CO,CE]{%TASKIDX%}
  - \fancyhead[LO,LE]{}
  - \fancyhead[RO,RE]{}
  - \fancyfoot[CO,CE]{%COPYRIGHTX%}
  - \fancyfoot[RO,LE]{\thepage}
  - \fancyfoot[LO,RE]{}
  - \fancypagestyle{plain}{\pagestyle{fancy}}
classoption: twoside
geometry: 'left=2cm,right=2cm,top=3cm,bottom=2cm'
---

```{r optionsChunk, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(
	eval = TRUE, 
	echo = TRUE,
	comment = "#",
	error = TRUE, 
	dpi = 150
)
options(warn = 1)
library(D4TAlink.light)
task <- initTask(project="%PROJECT%",
                 package="%PACKAGE%",
                 taskname="%TASK%",
                 sponsor="%SPONSOR%",
                 author="%AUTHOR%")
```

```{r loadLibraries, echo=FALSE}
# Load dependencies
library(stats)
```

\newpage

# Scope

In this section the scope / rationale of the task should be explained.

\newpage

# Input

The section list the information and data sources.

* List of patients (see email by JD dated 2022-05-01 17:12).
* List of assays (see task 20220102_loadAssays).

```{r loadInput, echo=FALSE}

# Code to load input data

# ta <- loadTask(task$project,task$package,"20220102_loadAssays)
# ass <- readBinary(ta,"assays")

```

\newpage

# Methods and Results

The results-section contains more details regarding the results of task X.

```{r consideredRCode, echo=TRUE}

# Chunk that contains the analysis R code.

```

\newpage

# Output

The section contains detailed information on output (incl. location).

* List of assays.

```{r saveOutput, echo=FALSE}

# Code to save data

# saveBinary(ass,ta,"assays")

```


\newpage

# Appendices

## Session information

```{r sessionInfo, echo=FALSE, results="asis"}

# In the appendix the session information is being printed for reproducibility.

sessionInfo()

```

